### 2020-04-23 readme.Rmd
update readme

  <!-- badges: start -->
  [![Travis build status](https://travis-ci.com/skiptoniam/qrbp.svg?branch=master)](https://travis-ci.com/skiptoniam/qrbp)
  [![Codecov test coverage](https://codecov.io/gh/skiptoniam/qrbp/branch/master/graph/badge.svg)](https://codecov.io/gh/skiptoniam/qrbp?branch=master)
  <!-- badges: end -->

## qrbp is tempory R package that will be ingested into [ecomix](https://github.com/skiptoniam/ecomix) for generating quasi random background points for multiple species Poisson point process models.

The package aims to setup a model matrix for point process modelling for mulitple species (marked) point processes. The package is based on the quadrature scheme proposed by Berman & Turner 1993, and Warton & Shepard 2010. The idea bebind this package is simple, provided a set of presences for a species (or multiple species) and a spatial region, we can generate generate a model matrix which can be included in a Poisson point process model.  The code does provide the ability to produce a background point dataset without the inclusion of presences (a dummy grid) or for single species (which was developed as a proof of concept for the multispecies approach).

We also provide the capacity to generate quasi-random points are an alternative to grid-based or random background point designs. Quasi-random (sampling) background points are an advanced form of spatially-balanced survey design or point stratification, that aims to reduce the frequency of placing samples close to each other (relative to simple randomisations or grid designs). A quasi-random background point design improves efficiency of background point sampling (and subsequent modelling) by reducing the amount of spatial auto-correlation between data implying that each sample is providing as much unique information as possible (Grafston & Tille, 2013) and thus reducing low errors for geostatistical prediction (Diggle & Ribeiro, 2007).

>>>>

[![Travis build status](https://travis-ci.com/skiptoniam/qrbp.svg?branch=master)](https://travis-ci.com/skiptoniam/qrbp)

[![Codecov test coverage](https://codecov.io/gh/skiptoniam/qrbp/branch/master/graph/badge.svg)](https://codecov.io/gh/skiptoniam/qrbp?branch=master)

## qrbp is temporary R package that will be ingested into [ecomix](https://github.com/skiptoniam/ecomix) for generating quasi random background points for multiple species Poisson point process models.

The package aims to setup a model matrix for point process modelling for multiple species (marked) point processes. The package is based on the quadrature scheme proposed by Berman & Turner 1993, and Warton & Shepard 2010. The idea behind this package is simple, provided a set of presences for a species (or multiple species) and a spatial region, we can generate generate a model matrix which can be included in a Poisson point process model.  The code does provide the ability to produce a background point data-set without the inclusion of presences (a dummy grid) or for single species (which was developed as a proof of concept for the multispecies approach).

We also provide the capacity to generate quasi-random points are an alternative to grid-based or random background point designs. Quasi-random (sampling) background points are an advanced form of spatially-balanced survey design or point stratification, that aims to reduce the frequency of placing samples close to each other (relative to simple randomization or grid designs). A quasi-random background point design improves efficiency of background point sampling (and subsequent modelling) by reducing the amount of spatial auto-correlation between data implying that each sample is providing as much unique information as possible (Grafston & Tille, 2013) and thus reducing low errors for geostatistical prediction (Diggle & Ribeiro, 2007).
